---
title: "Statistical Tests for Python Project"
output: html_document
date: "2024-02-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Texas P Values

These are the tests done for the various graphs for the Texas case study. They include: t-tests for differences between means, and Chi-squared tests to test whether the column variables are "significantly associated" with each other. 

```{r Texas}
Texas =  read.csv("~/NYCDSA/First Project/Git_Workspace/College_Scorecard_Data/Data/Texas_Retention.csv")
t.test(Overall.GPA ~ Retention, data = Texas)
#mean in group Not retained     mean in group Retained 
                  #3.023611                   3.113918 #p-value < 2.2e-16
t.test(High.School.GPA ~ Retention, data = Texas)
#mean in group Not retained     mean in group Retained 
                  #3.340696                   3.338728 #p-value = 0.8433
chisq.test(table(Texas$Change.in.GPA,Texas$Retention))
#p-value = 0.2266
chisq.test(table(Texas$Received.Financial.Aid,Texas$Retention))
#p-value = 3.376e-05
```
```{r Scoreboard Income Anovas (Ignore?)}
Scorecard$AVGFAMINC = as.numeric(as.character(Scorecard$AVGFAMINC))
Scorecard$FAMINC_IND = as.numeric(as.character(Scorecard$FAMINC_IND))
Scorecard$RET_FT4_POOLED = as.numeric(as.character(Scorecard$RET_FT4_POOLED))
#Scorecard$RET_FT4_POOLED = label_percent()(Scorecard$RET_FT4_POOLED)
#Anova(lm(C150_4_POOLED  ~ AVGFAMINC, data = Scorecard)) #P value < 2.2e-16
Anova(lm(RET_FT4_POOLED  ~ AVGFAMINC, data = Scorecard)) #P value < 2.2e-16
#Anova(lm(C150_4_POOLED  ~ FAMINC_IND, data = Scorecard)) #P value 0.07029 
Anova(lm(RET_FT4_POOLED  ~ FAMINC_IND, data = Scorecard)) #P value 0.006934
```
## Beta Regression For Family Individual Income and Retention

Beta regression is used when the dependent variable, y, is assumed 0,1 value.
```{r Scorecard Income Beta Regression/Individual}
Scorecard = read.csv("~/NYCDSA/First Project/Git_Workspace/College_Scorecard_Data/Data/Trimmed_Scorecard.csv")
Scorecard$PCTFLOAN = as.numeric(as.character(Scorecard$PCTFLOAN))
Scorecard$RET_FT4_POOLED = as.numeric(as.character(Scorecard$RET_FT4_POOLED))
Scorecard$AVGFAMINC = as.numeric(as.character(Scorecard$AVGFAMINC))
Scorecard$FAMINC_IND = as.numeric(as.character(Scorecard$FAMINC_IND))
#summary(gamlss(C150_4_POOLED ~ FAMINC_IND, data=na.omit(Scorecard)))
#T value -2.298    P value 0.0216
summary(gamlss(RET_FT4_POOLED ~ FAMINC_IND, data=na.omit(Scorecard)))
#T value 2.655 P value 0.00795
```
## Beta Regression For Family Average Income and Retention
```{r Scorecard Income Beta Regression/Family}
#summary(gamlss(C150_4_POOLED ~ AVGFAMINC, data=na.omit(Scorecard)))
#T value 17.18   P value <2e-16
summary(gamlss(RET_FT4_POOLED ~ AVGFAMINC, data=na.omit(Scorecard)))
#T value 21.59   P value <2e-16
```
## Beta Regression for Tuition and Retention

Tuition cost being for those from out of state and instate.
```{r Scorecard Tuition}
Scorecard$Instate_Tuition = as.numeric(as.character(Scorecard$Instate_Tuition))
Scorecard$Outstate_Tuition = as.numeric(as.character(Scorecard$Outstate_Tuition))
summary(gamlss(RET_FT4_POOLED ~ Instate_Tuition, data=na.omit(Scorecard)))
#T value 24.31   P value <2e-16
summary(gamlss(RET_FT4_POOLED ~ Outstate_Tuition, data=na.omit(Scorecard)))
#T value 32.17   P value <2e-16
```
## Beta Regression for SAT Scores and Retention
SAT score averages for all. 

```{r Scorecard SAT Scores}
Scorecard$SAT_AVG_ALL = as.numeric(as.character(Scorecard$SAT_AVG_ALL))
summary(gamlss(RET_FT4_POOLED ~ SAT_AVG_ALL, data=na.omit(Scorecard)))
#T Value 27.923   P Value <2e-16
```






