---
title: "Scorecard Negative Regression"
output: html_document
date: "2024-02-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(gamlss)
library(betareg)
library(dplyr)
library(tidyr)
```

## Anova for Students who receivied loans

Linear model Anova for Loan-Retention

```{r Scoreboard Debt Anovas}
Scorecard = read.csv("~/NYCDSA/First Project/Git_Workspace/College_Scorecard_Data/Data/Trimmed_Scorecard.csv")
Scorecard$PCTFLOAN = as.numeric(as.character(Scorecard$PCTFLOAN))
Scorecard$RET_FT4_POOLED = as.numeric(as.character(Scorecard$RET_FT4_POOLED))
#Anova(lm(RET_FT4_POOLED  ~ PCTFLOAN, data = Scorecard)) # SS 0.081, P value 0.08323
summary(gamlss(RET_FT4_POOLED ~ PCTFLOAN, data=na.omit(Scorecard)))
#T value, 1.721   P Value 0.0854
```

## Anova for Part-Time Students

Linear model Anova for Seeking Part Time-Retention

```{r Scorecard Part-Time}
Scorecard$Proportion_seeking_part_time = as.numeric(as.character(Scorecard$Proportion_seeking_part_time))
#Anova(lm(RET_FT4_POOLED  ~ Proportion_seeking_part_time, data = Scorecard)) 
#SS 8.847, P value < 2.2e-16
summary(gamlss(RET_FT4_POOLED ~ Proportion_seeking_part_time, data=na.omit(Scorecard)))
#-18.64   <2e-16
```
## Anova for Default Rate

Linear model Anova for Default Rate
```{r Scorecard Default Rate}
Scorecard$CDR2 = as.numeric(as.character(Scorecard$CDR2))
Anova(lm(RET_FT4_POOLED  ~ CDR2, data = Scorecard)) # SS 6.546, P value < 2.2e-16
summary(gamlss(RET_FT4_POOLED ~ CDR2, data=na.omit(Scorecard)))
#-16.73   <2e-16
```
## Anova % as a First Generation College Student

Linear model Anova for % First Generation
```{r Scorecard % First Generation}
Scorecard$FIRST_GEN = as.numeric(as.character(Scorecard$FIRST_GEN))
#Anova(lm(RET_FT4_POOLED  ~ FIRST_GEN, data = Scorecard)) # SS 7.263, P value < 2.2e-16
summary(gamlss(RET_FT4_POOLED ~ FIRST_GEN, data=na.omit(Scorecard)))
#-19.57   <2e-16
```
## Anova for Proportion of those Over 25

Linear model Anova for Over 25
```{r Scorecard Over 25}
Scorecard$UG25ABV = as.numeric(as.character(Scorecard$UG25ABV))
#Anova(lm(RET_FT4_POOLED  ~ UG25ABV, data = Scorecard)) # SS 4.393, P value < 2.2e-16
summary(gamlss(RET_FT4_POOLED ~ UG25ABV, data=na.omit(Scorecard)))
#-12.93   <2e-16
```
```{r}
Scorecard$C150_4_POOLED = as.numeric(as.character(Scorecard$C150_4_POOLED))
summary(gamlss(RET_FT4_POOLED ~ C150_4_POOLED, data=na.omit(Scorecard)))
```




